### 2020-03-03 thesis/content/chapter-related-work.tex
minor fixes + start of gnn section

Instead of mapping a graph into an explicitly defined vector space of fixed dimension, one can also do so implicitly by employing the kernel trick.
There is a large variety of so-called \acp{gk} to do this.
\acp{gk} can be used in combination with any kernelized learner, typically \acp{svm}, to solve the \ac{gcr} problem.
While there is a large variety of different \acp{gk}, we will focus on those that are based on the previously described family of \ac{wl} algorithms.

@@

>>>>

Instead of mapping a graph into an explicitly defined vector space of fixed dimension, one can also do so implicitly by employing the kernel trick.
There is a large variety of so-called \acp{gk} to do this.
\acp{gk} can be used in combination with any kernelized learner, typically \acp{svm}, to solve the \ac{gcr} problem.
While there is a large variety of different \acp{gk}~\cite{Kriege2020}, we will focus on those that are based on the previously described family of \ac{wl} algorithms.

@@

The last family of \ac{gcr} approaches we will look at is that of \acp{gnn}.
The idea to feed a graph into a \ac{nn} was first described by \citet{Gori2005}.
Since then many variants and extensions of that idea have been proposed~\cite{Wu2019}.
We will focus specifically on the so-called \acp{gcnn} which can be divided into two variants:
Spectral and spatial \acp{gcnn}.

\subsubsection{Spectral \acp{gcnn}}
The class of spectral \acp{gcnn} is motivated by spectral graph theory (see \cref{sec:related:character:spectral}).

\subsubsection{Spatial \acp{gcnn}}

\subsubsection{Graph Pooling}
